---
title: "Intro to Quarto"
format: html
duration: 2.5 hours
---

# Pre-workshop instructions

## While you wait for the workshop to begin... {.smaller}

-   Download and install the latest versions of R, RStudio, and Quarto:

    -   R: <https://cran.r-project.org>
    -   RStudio: <https://posit.co/download/rstudio-desktop>
    -   Quarto: <https://quarto.org/docs/get-started>

-   Install the following packages:

```{r}
#| label: pkg-list
#| eval: false

pkg_list <- c("tidyverse", "gt", "ggthemes", "palmerpenguins", "quarto", "here")
install.packages(pkg_list)
```

-   Download `exercises.zip` at <https://mine.quarto.pub/quarto-sdss/exercises.zip> and unzip it on your Desktop or somewhere you can easily locate on your computer. Then, go to RStudio \> File \> New Project \> Existing Directory and navigate to the unzipped `exercises` folder and create an RStudio project in there and open it.

Or, click [here](https://posit.cloud/spaces/377666/join?access_code=kp0V37Moc2WynUu8xZc_9c-sGFuEAqfDvXdhWTEX) to join the Posit Cloud space for the workshop.

::: aside
A few of the features we'll demo may not work on Posit Cloud since the Quarto version is a bit behind, but you should be able to follow \>95% of the workshop there.
:::

# Welcome

## Room info {.smaller}

-   WiFi: Curio Meeting / 1820

-   Emergency exits behind you

-   Restrooms: Out the door and turn right, then men's to the left, women's to the right

## Code of Conduct {.smaller}

> The American Statistical Association (ASA) is committed to providing an atmosphere in which personal respect and intellectual growth are valued and the free expression and exchange of ideas are encouraged. Consistent with this commitment, it is the policy of the ASA that all participants in ASA activities enjoy a welcoming environment free from unlawful discrimination, harassment, and retaliation. We strive to be a community that welcomes and supports people of all backgrounds and identities. This includes, but is not limited to, members of any race, ethnicity, culture, national origin, color, immigration status, social and economic class, educational level, sex, sexual orientation, gender identity and expression, age, size, family status, political belief, religion, and mental and physical ability.

::: aside
[ASA Code of Conduct](https://www.amstat.org/meetings/code-of-conduct)
:::

## Expected Behavior {.smaller}

> -   Model and support the norms of respect necessary to promote the conditions for healthy exchange of scientific ideas.
>
> -   In speech or conduct, do not insult or disparage other participants.
>
> -   Be conscious of hierarchical structures, specifically the existence of stark power differentials between students, early career statisticians and established career statisticians---noting that fear of retaliation from more established statisticians can make it difficult for students and early career statisticians to express discomfort, rebuff unwelcome advances, and report violations of the conduct policy.
>
> -   Be sensitive to indications that may suggest that individuals are feeling unwelcome.

::: aside
[ASA Code of Conduct](https://www.amstat.org/meetings/code-of-conduct)
:::

## About Me

## Workshop Goals

This workshop will be a little bit different to your standard Intro to Quarto workshop.

We will focus on:

- features of Quarto that can help you document research code and data:
    - incorporate existing text files (scripts, table outputs etc.) <!-- includes -->
    - reference management -- e.g. in-line citations, cross-references, figure and table numbers <!--- citations -->
    - generate summary tables and overviews from listing files <!--- listings --->
- how to publish and share Quarto projects online
- giving you enough skills in Quarto, git, GitHub and R to incorporate some of these learnings in your existing workflows

I will assume:

- you regularly write scripts in at least one computational language (e.g. STATA, R, python)
- you know at least basic LaTex
- you work with small-to-medium sized datasets which can be compressed into reasonable sized downloads.

---

We will get a taste of:

- how quarto works under the hood, including how it generates LaTex files
- 

We will not cover:

- computational workflows in Quarto (R, Python, Julia, Observable)
- version control using git

## About You

- fill in details about the person next to you at this github issue

```{r}
#| echo: false

countdown(minutes = 2)
```

<!--- Live coding : LISTING PAGE --->

-   Hello Quarto // 10mins showcase, showoff! --- stop installation
    -   give extra time to first exercise; we will help you!
-   Single Documents
-   Articles (with journal templates)
-   my-first-document.qmd